Explaining Noord-Holland house prices

### 2023-04-04 Paper/paper.Rmd

@@

\begin{figure*}
  \centering
  \includegraphics[width=.6\linewidth]{figures/plot.pdf}
  \caption{This is a figure.}
\end{figure*}

>>>>

\maketitle

@@

```{=latex}
\begin{figure*}[ht]
  \centering
  \includegraphics[width=.6\linewidth]{figures/plot.pdf}
  \caption{This is a figure.}
\end{figure*}

```{r eval=FALSE, include=FALSE}
library(xtable)
xtable(tail(mtcars))
```

```{=latex}
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrr}
  \hline
 & mpg & cyl & disp & hp & drat & wt & qsec & vs & am & gear & carb \\ 
  \hline
Porsche 914-2 & 26.00 & 4.00 & 120.30 & 91.00 & 4.43 & 2.14 & 16.70 & 0.00 & 1.00 & 5.00 & 2.00 \\ 
  Lotus Europa & 30.40 & 4.00 & 95.10 & 113.00 & 3.77 & 1.51 & 16.90 & 1.00 & 1.00 & 5.00 & 2.00 \\ 
  Ford Pantera L & 15.80 & 8.00 & 351.00 & 264.00 & 4.22 & 3.17 & 14.50 & 0.00 & 1.00 & 5.00 & 4.00 \\ 
  Ferrari Dino & 19.70 & 6.00 & 145.00 & 175.00 & 3.62 & 2.77 & 15.50 & 0.00 & 1.00 & 5.00 & 6.00 \\ 
  Maserati Bora & 15.00 & 8.00 & 301.00 & 335.00 & 3.54 & 3.57 & 14.60 & 0.00 & 1.00 & 5.00 & 8.00 \\ 
  Volvo 142E & 21.40 & 4.00 & 121.00 & 109.00 & 4.11 & 2.78 & 18.60 & 1.00 & 1.00 & 4.00 & 2.00 \\ 
   \hline
\end{tabular}
\end{table*}
